### 2015-05-11 CVPR/quals2report.tex
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

\documentclass[10pt,letterpaper]{report}

@@

@@

\chapter{Appendix}
\label{ref:appendix}
\input{../Paper/suplementarymaterial.tex}

>>>>

\documentclass[letterpaper]{report}

@@

\newcommand{\EnergyBBox}{{\pEnergy{bbox}}}
\newcommand{\EnergyTrack}{{ \pEnergy{track}}}
\newcommand{\EnergyTrackNoOcc}{{\pEnergy{trackNoOcc}}}
\newcommand{\EnergyLane}{{\Energy{lane}}}
\newcommand{\EnergySize}{{\Energy{size}}}
\newcommand{\EnergyDyn}{{\Energy{dyn}}}
\newcommand{\EnergyDynHol}{{\Energy{dyn-hol}}}
\newcommand{\EnergyDynOri}{{\Energy{dyn-ori}}}
\newcommand{\EnergyDynVel}{{\Energy{dyn-vel}}}

\newcommand{\xmin}{\xymin{x}}
\newcommand{\xmax}{\xymax{x}}
\newcommand{\ymin}{\xymin{y}}
\newcommand{\ymax}{\xymax{y}}

@@

\chapter{Future Work}

We have come up with model of Object detection energy with occlusion, and our plan is evaluate it
and integrate it with the model.

\section{Object detection energy with occlusion}

Object detection is usually followed by non-maximal suppression that results in
discarding similar bounding boxes. When we are jointly optimizing detections
with other cues, it is not usually desirable to go with a single bounding box.
Hence, we keep all the bounding box detections by approximating them with
multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
%
\begin{align}
  S(\bb{i}) = \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
  (\bb{i}-\mu^{(d)}_k))
\end{align}
%
to detection scores, by non-linear error minimization with initialization from
non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
4D vector representing a single bounding box as $[\minx, \miny, \maxx,
\maxy]^\top$. The optimization is constrained with symmetry and positive
definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\subsection{Detection scores with occlusion reasoning} 
With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
compute the probability of a point $\mathbf{u}$ on image be occluded assuming
the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
\end{align}

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
%One of the simplest ways will be to scale the appropriate diagonal element of
%$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
%does not model explain the affect of occlusion on the non diagonal terms.
%Hence, we choose a covariance addition model where we compute a occlusion
%covariance matrix, that provides a measure of occlusion in each direction.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
%
%\begin{align}
%\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{align}
  S'(\bb{i}) =
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}

The energy of detection scores is simply take to be the inverse of the detection score.
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
\end{align}

\chapter{Appendix}
\label{sec:appendix}
\input{../Paper/suplementarymaterial.tex}

### 2015-05-11 presentation/intro.tex
Latest version of presentation.
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

@@

\begin{frame}{Problem}
  % Need a flowchart that describes the input and desired output of the system
 \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
 \newlength{\units}
 \setlength{\units}{0.8cm}
  \scriptsize{
    \input{Source/problemflowchart.tex}
  }
\end{frame}

% \begin{frame}{Problem}
%   \visible<-1>{
%     \begin{tikzpicture}
%       \node[anchor=south west,inner sep=0] (image) at (0,0)
%       {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
%       \fill[color=white] (image.south west) rectangle (image.east);
%     \end{tikzpicture}
%   }
% \end{frame}
\begin{frame}{Problem}

  \def\arrow{
    (0,0) -- ++(1,0)
    -- ++(0,1) -- ++(0.3, 0)
    -- ++(-0.8, 1) -- ++(-0.8, -1) -- ++(0.3, 0) -- ++(0, -1) }

  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] (image) at (0,0)
    {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
      \fill[color=red,scale=0.05,shift={(10,11)},rotate=180,]\arrow;
    \end{scope}
  \end{tikzpicture}
\end{frame}

>>>>

\begin{frame}{Motivation: Google car}

  \begin{tikzpicture}
    \node [anchor=north west,inner sep=0] (img) at (0,0) 
    {\includegraphics[width=0.42\textwidth, trim=4cm 00cm 1cm 0cm,clip]{graphics/google-laser-scan-cost.jpg}};
    \begin{scope}[x=(img.north east),y=(img.south west)] 
      \coordinate (velc) at (0.25, 0.10);
      \draw [very thick,red] (velc) ellipse (0.25 and 0.10);
      %\draw [->,red] (0,0) -- (1, 0) node {X};
      %\draw [->,red] (0,0) -- (0, 1) node {Y};
    \end{scope}
  \end{tikzpicture}
  \includegraphics[width=0.50\textwidth, trim=3cm 00cm 3cm 0cm,clip]{graphics/google-laser-scan.jpg}
  \pause

  But Velodyne costs \tikz[remember picture] \node [anchor=north,inner sep=0] (cost) at (0,0) {\$75k};
\end{frame}

\begin{frame}{Can we do it with cameras? Stereo or Monocular}
  \begin{columns}
    \begin{column}{0.48\textwidth}
      \centering
      Left Camera\\
      \includemedia[label=stereoleft,
        width=\textwidth,
        activate=pageopen,
        addresource=graphics/upto61_quat.mp4,
        flashvars={
          source=graphics/upto61_quat.mp4
          &autoPlay=true
          &loop=true             % loop video
          &scaleMode=letterbox   % preserve aspect ratio while scaling the video
        }
      ]{\includegraphics{graphics/0000000061_raw.png}}{VPlayer.swf}
    \end{column}
    \begin{column}{0.48\textwidth}
      \centering
      Right Camera\\
      \includemedia[label=stereoright,
        width=\textwidth,
        activate=pageopen,
        addresource=graphics/upto61_quat_right.mp4,
        flashvars={
          source=graphics/upto61_quat_right.mp4
          &autoPlay=true
          &loop=true             % loop video
          &scaleMode=letterbox   % preserve aspect ratio while scaling the video
        }
      ]{\includegraphics{graphics/0000000061_right.png}}{VPlayer.swf}
    \end{column}
  \end{columns}

  Stereo cameras neeed to be recaliberated

  And the depth range of stereo cameras are limited

  So after certain depth stereo is same as monocular
\end{frame}

@@

\begin{frame}{Sample input and output}
  \def\arrow{
    (0,0) -- ++(1,0)
    -- ++(0,1) -- ++(0.3, 0)
    -- ++(-0.8, 1) -- ++(-0.8, -1) -- ++(0.3, 0) -- ++(0, -1) }
    \begin{tikzpicture}
      \node[anchor=south west,inner sep=0] (image) at (0,0)
      {
        \includemedia[label=sampleinput,
          width=\textwidth,
          activate=pageopen,
          addresource=graphics/initonly_half.mp4,
          flashvars={
            source=graphics/initonly_half.mp4
            &autoPlay=true
            &loop=true             % loop video
            &scaleMode=letterbox   % preserve aspect ratio while scaling the video
          }
        ]{
        \includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}    }{VPlayer.swf}
      };
      \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \fill[color=red,scale=0.05,shift={(10,11)},rotate=180,]\arrow;
      \end{scope}
    \end{tikzpicture}

\end{frame}

\begin{frame}{Intermediate inputs}
  % Need a flowchart that describes the input and desired output of the system
 \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
 \setlength{\units}{0.8cm}
  \scriptsize{
    \problemflowchart{}{}{}{}{}
  }
\end{frame}

% \begin{frame}{Problem}
%   \visible<-1>{
%     \begin{tikzpicture}
%       \node[anchor=south west,inner sep=0] (image) at (0,0)
%       {\includegraphics[width=\textwidth]{graphics/0000000061_bevdown.png}};
%       \fill[color=white] (image.south west) rectangle (image.east);
%     \end{tikzpicture}
%   }
% \end{frame}

### 2015-05-11 presentation/pointTrackEnergyWithOccFigure.tex
Latest version of presentation. Could not add fading because it makes my latex to crash with segmentation fault.

\begin{tikzpicture}[x=0.8cm,y=0.8cm,3d/perspective eye={4,4,-10},ptstyle/.style={fill=#1,draw,circle,inner sep=1.5pt}]
    \input{Source/twocuboids.tex}
    \draw [->, very thick, draw=blue] (pta4) --  +(90:1) node [anchor=south,align=center] {$a^1(\lambda) = 0$\\$a^2(\lambda) = 1$};
    \draw [->, very thick, draw=red!50!blue] (pta-8) --  +(170:1.4) node [anchor=south,align=center] {$a^1(\lambda) = 0.5$\\$a^2(\lambda) = 0.5$};
    \draw [->, very thick, draw=red] ($(ptb-8)+(.5,-.8)$) --  +(-60:.8) node [anchor=north,align=center] {$a^1(\lambda) = 1$\\$a^2(\lambda) = 0$};
   \begin{scope}[shift={(4,-2)}]
     \path [fill=blue!20,draw] (0,0) ellipse (1.2 and 0.7);
     \path [fill=green!20,draw] (3,0) ellipse (1.2 and 0.7);
     \coordinate (o) at (-2,-1);
     \draw(o) edge [->,very thick] node (xa) {} +(6, 0);
     \node at ($(xa) + (0, -0.2)$) {Depth from camera ($\lambda$)};
     \draw(o) edge [->,very thick] node (ya) {} +(0, 2);
     \node [rotate=90]at ($(ya) + (-0.2, 0)$) {$a^{(1j)}(\lambda)$};
\draw [thick,red] plot [smooth] coordinates {($(o)+(0,1.8)$) ($(o)+(0.2,1.8)$) ($(o) + (0.8, 1.7)$) ($(o)+(1.4,0.3)$) ($(o)+(3.8,0.2)$)($(o)+(4.4,0.1)$) ($(o)+(6.1,0.1)$)};
   \end{scope}
\end{tikzpicture}

>>>>

\begin{tikzpicture}[x=0.8cm,y=0.8cm,3d/perspective eye={4,4,-10},ptstyle/.style={fill=#1,draw,circle,inner sep=1.5pt}]
    \input{Source/twocuboids.tex}
    \draw [->, very thick, draw=blue] (pta4) --  +(90:1) node [anchor=south,align=center] {$a^{1j}(\lambda) = 0$\\$a^{2j}(\lambda) = 1$};
    \draw [->, very thick, draw=red!50!blue] (pta-8) --  +(170:1.4) node [anchor=south,align=center] {$a^{1j}(\lambda) = 0.5$\\$a^{2j}(\lambda) = 0.5$};
    \draw [->, very thick, draw=red] ($(ptb-8)+(.5,-.8)$) --  +(-60:.8) node [anchor=north,align=center] {$a^{1j}(\lambda) = 1$\\$a^{2j}(\lambda) = 0$};
   \begin{scope}[shift={(4,-2)}]
     \path [fill=blue!20,draw] (0,0) ellipse (1.2 and 0.7);
     \path [fill=green!20,draw] (3,0) ellipse (1.2 and 0.7);
     \coordinate (o) at (-2,-1);
     \draw(o) edge [->,very thick] node (xa) {} +(6, 0);
     \node at ($(xa) + (0, -0.2)$) {Depth from camera ($\lambda$)};
     \draw(o) edge [->,very thick] node (ya) {} +(0, 2);
     \node [rotate=90]at ($(ya) + (-0.2, 0)$) {$a^{(1j)}(\lambda)$};
\draw [thick,red] plot [smooth] coordinates {($(o)+(0,1.8)$) ($(o)+(0.2,1.8)$) ($(o) + (0.8, 1.7)$) ($(o)+(1.4,0.3)$) ($(o)+(3.8,0.2)$)($(o)+(4.4,0.1)$) ($(o)+(6.1,0.1)$)};
   \end{scope}
\end{tikzpicture}
